\documentclass[aos, preprint]{imsart}
% \documentclass{article}

\RequirePackage[OT1]{fontenc}
\RequirePackage{amsthm,amsmath}
\RequirePackage[numbers]{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% settings
\pubyear{2019}
\volume{0}
\issue{0}
\firstpage{1}
\lastpage{48}

% add packages
\usepackage{enumitem}
\usepackage{amsfonts,graphicx,bbm}
%\usepackage[square,numbers]{natbib}
%\bibliographystyle{plain}
\usepackage{array,booktabs}
%\usepackage[margin=1.25in]{geometry}

%
% My definitions:
%
\def\bbN{{\mathbb N}}
\def\bbZ{{\mathbb Z}}
\def\bbR{{\mathbb R}}
\def\bbC{{\mathbb C}}

\def\P{{\mathbb P}}
\def\E{{\mathbb E}}

\newcommand{\var}{{\rm {Var}}}
\newcommand{\cov}{{\rm {Cov}}}

\def\N{\mathbb N}
\def\R{\mathbb R}
\def\Z{\mathbb Z}
\usepackage{bm}
\renewcommand\vec[1]{{\bm #1}}

\def\alert#1{\fbox{#1}}
\def\what{\widehat}
\def\noi{\noindent}
\def\MSE{{\rm m.s.e.}}
\newcommand\comment[1]{{}}
\def\refeq#1{(\ref{e:#1})}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\newcommand\version[2]{{#1}} % The short version of the paper
%\newcommand\version[2]{{#2}} % The long version of the paper

%\startlocaldefs
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
% my defs
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{assumption}{Assumption}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
%\endlocaldefs



\begin{document}

\begin{frontmatter}
\title{\Large{Five Shades of Grey: Phase Transitions in High-dimensional Multiple Testing}} %\thanksref{T1}} 
\runtitle{Phase Transitions in High-dimensional Multiple Testing} % and Multiple Testing for Categorical Data}
%\thankstext{T1}{Footnote to the title with the `thankstext' command.}

\begin{aug}
\author{\fnms{Zheng} \snm{Gao}\thanksref{t1}\ead[label=e1]{gaozheng@umich.edu}}
%\and
%\author{\fnms{Second} \snm{Author}}%\thanksref{t3}\ead[label=e2]{second@somewhere.com}}

\address{Department of Statistics, University of Michigan, Ann Arbor, USA\\
\printead{e1}}

\thankstext{t1}{This research is supported by NSF Grant DMS-1830293, Algorithms for Threat Detection.}
%\thankstext{t2}{First supporter of the project}
%\thankstext{t3}{Second supporter of the project}
\runauthor{Z. Gao}

\affiliation{University of Michigan}

\end{aug}

\begin{abstract}
We are motivated by marginal screenings of categorical variables, and study high-dimensional multiple testing problems where test statistics have approximate chi-square distributions.
We characterize four new phase transitions in high-dimensional chi-square models, and derive the signal sizes necessary and sufficient for statistical procedures to simultaneously control false discovery (in terms of family-wise error rate or false discovery rate) and missed detection (in terms of family-wise non-discovery rate or false non-discovery rate) in large dimensions.
% 1) approximately, and 2) exactly select the set of relevant features in large dimensions.
Remarkably, degrees of freedom in the chi-square distributions do not affect the boundaries in all four phase transitions.
Several well-known procedures are shown to attain these boundaries.
Two new phase transitions are also identified in the Gaussian location model under one-sided alternatives.

We then elucidate on the nature of signal sizes in association tests by characterizing its relationship with marginal frequencies, odds ratio, and sample sizes in $2\times2$ contingency tables.
% in common association tests for binary traits.
% Specifically, detection of rare genetic variants associated with the outcomes requires more samples compared to common variants. 
% Specifically, the difficulty in detecting associations between genetic variants and phenotype traits is quantified in terms of the signal sizes.
% Specifically, the amount of signal per sample is inherently smaller when rare variants are present. 
% In other words, 
% Further, case prevalence in the recruited subjects plays a role, while case prevalence in the population is irrelevant.
% We provide explicit formulas for power calculations, as well as software tools for finding the optimal study designs.
This allows us to illustrate an interesting manifestation of the phase transition phenomena in genome-wide association studies (GWAS).
We also show, perhaps surprisingly, that given total sample sizes, balanced designs in such association studies rarely deliver optimal power. 
% for detecting rare genetic variants with high odds ratios.

% The phase transition phenomena are demonstrated with numerical simulations, and with empirical evidence from GWAS.
% data from the NHGRI-EBI GWAS catalog.
\end{abstract}

\begin{keyword}[class=MSC]
%\kwd[Primary ]{62G10, 62G20}
\kwd{62G10, 62G20}
%\kwd[; secondary ]{60K35}
\end{keyword}

\begin{keyword}
\kwd{Multiple testing}
\kwd{asymptotic optimality}
\kwd{family-wise error rate (FWER) control}
\kwd{false discovery rate (FDR) control}
\kwd{categorical data analysis}
\kwd{association tests}
\end{keyword}
\tableofcontents
\end{frontmatter}

\section{Introduction}
\label{sec:intro}
\input{1-introduction.tex}

\section{Statistical risks, procedures, and the asymptotic regime}
\label{sec:setup}
\input{2-setup.tex}

\section{Phase transitions of multiple testing in the chi-square models}
\label{sec:chisq-boundaries}
\input{3-boundary.tex}

\section{The phase transition phenomena in GWAS}
\label{sec:signal-size-odds-ratio}
\input{4-odds-ratios.tex}

\section{Phase transitions in the Gaussian additive error model}
\label{sec:additive-error-model-boundaries}
\input{5-additive-error-model.tex}

\section{Numerical illustrations}
\label{sec:numerical}
\input{6-numerical-experiments.tex}

\section{Discussions}
\label{sec:discussions}
\input{7-discussion.tex}

\appendix

\section{A review of common procedures in multiple testing}
\label{sec:procedures}
\input{A1-procedures.tex}

\section{Proofs}
\label{sec:proofs}
\input{A2-proofs.tex}


\section*{Acknowledgements}
I thank Professor Stilian Stoev for encouraging me to pursue the current project, and for his most generous support.
I also thank Jingshen Wang and Yuanzhi Li for their helpful comments and thoughtful feedback, as well as Rafail Kartsioukas and Jinqi Shen for their careful proof-reading of the manuscript.
This research is supported by NSF Grant DMS-1830293, Algorithms for Threat Detection.
% \bibliographystyle{plainnat}
\bibliographystyle{imsart-nameyear}
\bibliography{references}


% \begin{thebibliography}{9}
% 
% \bibitem{r1}
% \textsc{Billingsley, P.} (1999). \textit{Convergence of
% Probability Measures}, 2nd ed.
% Wiley, New York.
% \MR{1700749}
% 
% 
% \bibitem{r2}
% \textsc{Bourbaki, N.}  (1966). \textit{General Topology}  \textbf{1}.
% Addison--Wesley, Reading, MA.
% 
% \bibitem{r3}
% \textsc{Ethier, S. N.} and \textsc{Kurtz, T. G.} (1985).
% \textit{Markov Processes: Characterization and Convergence}.
% Wiley, New York.
% \MR{838085}
% 
% \bibitem{r4}
% \textsc{Prokhorov, Yu.} (1956).
% Convergence of random processes and limit theorems in probability
% theory. \textit{Theory  Probab.  Appl.}
% \textbf{1} 157--214.
% \MR{84896}
% 
% \end{thebibliography}

\end{document}
